%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Thin Sectioned Essay
% LaTeX Template
% Version 1.0 (3/8/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original Author:
% Nicolas Diaz (nsdiaz@uc.cl) with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper, 11pt]{article} % Font size (can be 10pt, 11pt or 12pt) and paper size (remove a4paper for US letter paper)

\usepackage{graphicx}   % for EPS use the graphics package instead
\usepackage{epstopdf}
\usepackage[protrusion=true,expansion=true]{microtype} % Better typography
\usepackage{wrapfig} % Allows in-line images
\usepackage{longtable}
\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

\usepackage{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Required for accented characters
\usepackage{indentfirst}
\usepackage[table]{xcolor}
\usepackage{marvosym}
\usepackage{subfigure}
\usepackage{multirow}
\linespread{1} % Change line spacing here, Palatino benefits from a slight increase by default

\makeatletter
\renewcommand\@biblabel[1]{\textbf{#1.}} % Change the square brackets for each bibliography item from '[1]' to '1.'
\renewcommand{\@listI}{\itemsep=0pt} % Reduce the space between items in the itemize and enumerate environments and the bibliography

\renewcommand{\maketitle}{ % Customize the title - do not edit title and author name here, see the TITLE block below

\begin{flushright} % Right align
{\LARGE\@title} % Increase the font size of the title

\vspace{20pt} % Some vertical space between the title and author name

{\large\@author} % Author name
\vspace{15pt}
\\\@date % Date

\vspace{20pt} % Some vertical space between the author block and abstract
\end{flushright}
}

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------



\title{Indoor Big Data \textit{Reading List}} % Subtitle
\author{\textsc{Database Laboratory} % Author
, {\textit{Zhejiang University}}} % Institution

\date{\today} % Date

%----------------------------------------------------------------------------------------

\begin{document}

\maketitle % Print the title section


%----------------------------------------------------------------------------------------
%	ABSTRACT AND KEYWORDS
%----------------------------------------------------------------------------------------

%\renewcommand{\abstractname}{Summary} % Uncomment to change the name of the abstract to something else

%----------------------------------------------------------------------------------------
%	ESSAY BODY
%----------------------------------------------------------------------------------------

\section{Indoor Positioning \& Systems}

\renewcommand{\refname}{}

\vspace{-25pt} % Beamer does not support BibTeX so references must be inserted manually as below
\begin{thebibliography}{99}

\bibitem{liu2007survey}
H.~Liu, H.~Darabi, P.~Banerjee, J.~Liu.
\newblock Survey of wireless indoor positioning techniques and systems.
\newblock In {\em IEEE Transactions on Systems, Man, and Cybernetics}, pp. 1067--1080, 2007.

\bibitem{bessho2009location}
M.~Bessho, N.~Koshizuka, S.~Kobayashi, K.~Sakamura.
\newblock Location systems for ubiquitous computing.
\newblock In {\em Journal of IEICE}, pp. 249--255, 2009.

\bibitem{gu2009survey}
Y.~Gu, A.~Lo, I.~Niemegeers.
\newblock A survey of indoor positioning systems for wireless personal networks.
\newblock In {\em IEEE Communications surveys \& tutorials}, pp. 13--32, 2009.

\bibitem{hansen2010algorithmic}
R.~Hansen, R.~Wind, C.S.~Jensen, B.~Thomsen.
\newblock Algorithmic strategies for adapting to environmental changes in 802.11 location fingerprinting.
\newblock In {\em IPIN}, pp. 1--10, 2010.

\bibitem{ganu2004infrastructure}
S.~Ganu, AS.~Krishnakumar, P.~Krishnan.
\newblock Infrastructure-based location estimation in WLAN networks.
\newblock In {\em WCNC}, pp. 465--470, 2004.

\bibitem{hansen2013smartcampusaau}
R.~Hansen, B.~Thomsen, L.~Thomsen, F.~Adamsen.
\newblock SmartCampusAAU--An Open Platform Enabling Indoor Positioning and Navigation.
\newblock In {\em MDM}, pp. 33--38, 2013.

\end{thebibliography}

%----------------------------------------------------------------------------------------

\section{Indoor Space Modeling \& Spatial Indices}

\vspace{-25pt} % Beamer does not support BibTeX so references must be inserted manually as below
\begin{thebibliography}{99}

\bibitem{worboys2011modeling}
M.~Worboys.
\newblock Modeling indoor space.
\newblock In {\em {SIGSPATIAL}}, pp. 1--6, 2011.

\bibitem{DBLP:conf/mdm/JensenLY09}
C.~S. Jensen, H.~Lu, and B.~Yang.
\newblock Graph model based indoor tracking.
\newblock In {\em {MDM}}, pp. 122--131, 2009.

\bibitem{DBLP:conf/cikm/YangLJ09}
B.~Yang, H.~Lu, and C.~S. Jensen.
\newblock Scalable continuous range monitoring of moving objects in symbolic
  indoor space.
\newblock In {\em CIKM}, pp. 671--680, 2009.

\bibitem{DBLP:conf/edbt/YangLJ10}
B.~Yang, H.~Lu, and C.~S. Jensen.
\newblock Probabilistic threshold k nearest neighbor queries over moving
  objects in symbolic indoor space.
\newblock In {\em EDBT}, pp. 335--346, 2010.

\bibitem{DBLP:conf/icde/LuYCJ11}
H.~Lu, B.~Yang, and C.~S. Jensen.
\newblock Spatio-temporal Joins on Symbolic Indoor Tracking Data.
\newblock In {\em {ICDE}}, pp. 816--827, 2011.

\bibitem{DBLP:conf/icde/LuCJ12}
H.~Lu, X.~Cao, and C.~S. Jensen.
\newblock A foundation for efficient indoor distance-aware query processing.
\newblock In {\em ICDE}, pp. 438--449, 2012.

\bibitem{DBLP:conf/icde/XieLP13}
X.~Xie, H.~Lu, and T.~B. Pedersen.
\newblock Efficient distance-aware query evaluation on indoor moving objects.
\newblock In {\em ICDE}, pp. 434--445, 2013.

\bibitem{boysen2014constructing}
M.~Boysen, C.~de Haas, H.~Lu, X.~Xie, A.~Pilvinyte.
\newblock Constructing indoor navigation systems from digital building information.
\newblock In {\em ICDE}, pp. 1194--1197, 2014.

\bibitem{xie2015distance}
X.~Xie, H.~Lu, and T.~B. Pedersen.
\newblock Distance-aware join for indoor moving objects.
\newblock In {\em TKDE}, pp. 428--442, 2015.

\end{thebibliography}

%----------------------------------------------------------------------------------------

\section{Indoor Data Cleansing}

\vspace{-25pt} % Beamer does not support BibTeX so references must be inserted manually as below
\begin{thebibliography}{99}

\bibitem{chen2010leveraging}
H.~Chen, W-S.~Ku, H.~W and M-T.~S.
\newblock Leveraging spatio-temporal redundancy for RFID data cleansing.
\newblock In {\em SIGMOD}, pp. 51--62, 2010.

\bibitem{baba2013spatiotemporal}
A.I.~Baba, H.~Lu, X.~Xie, T.B.~Pedersen.
\newblock Spatiotemporal data cleansing for indoor RFID tracking data.
\newblock In {\em MDM}, pp. 187--196, 2013.

\bibitem{baba2013graph}
A.I.~Baba, H.~Lu, T.B.~Pedersen, X.~Xie.
\newblock A graph model for false negative handling in indoor RFID tracking data.
\newblock In {\em SIGSPATIAL}, pp. 464--467, 2013.

\bibitem{baba2014handling}
A.I.~Baba, H.~Lu, T.B.~Pedersen, X.~Xie.
\newblock Handling false negatives in indoor RFID data.
\newblock In {\em MDM}, pp. 117--126, 2014.

\bibitem{DBLP:conf/edbt/FazzingaFFP14}
B.~Fazzinga, S.~Flesca, F.~Furfaro, F.~Parisi.
\newblock Cleaning Trajectory Data of RFID-monitored Objects through Conditioning under Integrity Constraints.
\newblock In {\em EDBT}, pp. 379--390, 2014.

\bibitem{fazzinga2014offline}
B.~Fazzinga, S.~Flesca, F.~Furfaro, F.~Parisi.
\newblock Offline cleaning of RFID trajectory data.
\newblock In {\em SSDBM}, pp. 5:1 -- 5:12, 2014.

\bibitem{DBLP:conf/edbt/FazzingaFFP14}
B.~Fazzinga, S.~Flesca, F.~Furfaro, F.~Parisi.
\newblock Cleaning Trajectory Data of RFID-monitored Objects through Conditioning under Integrity Constraints.
\newblock In {\em EDBT}, pp. 379--390, 2014.

\bibitem{baba2016learning}
A.I.~Baba, M.~Jaeger, H.~Lu, T.B.~Pedersen, W-S.~Ku, X.~Xie.
\newblock Learning-Based Cleansing for Indoor RFID Data.
\newblock In {\em SIGMOD}, 2016.

\end{thebibliography}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------

\section{Indoor Movement \& Trajectory Management}

\vspace{-25pt} % Beamer does not support BibTeX so references must be inserted manually as below
\begin{thebibliography}{99}

\bibitem{jensen2010indoor}
C.S~Jensen H.~Lu and B.~Yang.
\newblock Indoor-A New Data Management Frontier.
\newblock In {\em IEEE Data Eng. Bull.}, pp. 12--17, 2010.

\bibitem{jeung2014managing}
H.~Jeung, H.~Lu, T.B.~Pedersen, S.~Sathe, M L.~Yiu.
\newblock Managing evolving uncertainty in trajectory databases.
\newblock In {\em TKDE}, pp. 1692--1705, 2014.

\bibitem{hornsby2002modeling}
K.~Hornsby, M.J.~Egenhofer.
\newblock Modeling moving objects over multiple granularities.
\newblock In {\em Annals of Mathematics and Artificial Intelligence}, pp. 177--194, 2002.

\bibitem{trajcevski2004managing}
G.~Trajcevski, O.~Wolfson, K.~Hinrichs, S.~Chamberlain.
\newblock Managing uncertainty in moving objects databases.
\newblock In {\em TODS}, pp. 463--507, 2004.

\bibitem{lu2016finding}
H.~Lu, C.~G, B.~Yang, C.S.~Jensen.
\newblock Finding frequently visited indoor POIs using symbolic indoor tracking data
\newblock In {\em EDBT}, 2016.



\end{thebibliography}

\end{document}
