%------------------------------------------------

\begin{frame}[allowframebreaks]
\frametitle{References}

\begin{thebibliography}{99} % Beamer does not support BibTeX so references must be inserted manually as below
\bibliographystyle{abbrv}
\fsize{

\bibitem{jeung2014managing}
H.~Jeung, H.~Lu, T.B.~Pedersen, S.~Sathe, M L.~Yiu.
\newblock Managing evolving uncertainty in trajectory databases.
\newblock In {\em TKDE}, pp. 1692--1705, 2014.

\bibitem{pfoser1999capturing}
D.~Pfoser, C.S.~Jensen.
\newblock Capturing the uncertainty of moving-object representations.
\newblock In {\em SSD}, pp. 111--131, 1991.

\bibitem{hornsby2002modeling}
K.~Hornsby, M.J.~Egenhofer.
\newblock Modeling moving objects over multiple granularities.
\newblock In {\em Annals of Mathematics and Artificial Intelligence}, pp. 177--194, 2002.

\bibitem{kuijpers2007trajectory}
B.~Kuijpers, W.~Othman.
\newblock Trajectory databases: Data models, uncertainty and complete query languages.
\newblock In {\em ICDT}, pp. 224--238, 2007.

\bibitem{frentzos2009effect}
E.~Frentzos, K.~Gratsias, Y.~Theodoridis.
\newblock On the effect of location uncertainty in spatial querying.
\newblock In {\em TKDE}, pp. 366--383, 2009.

\bibitem{trajcevski2004managing}
G.~Trajcevski, O.~Wolfson, K.~Hinrichs, S.~Chamberlain.
\newblock Managing uncertainty in moving objects databases.
\newblock In {\em TODS}, pp. 463--507, 2004.

\bibitem{trajcevski2002geometry}
G.~Trajcevski, O.~Wolfson, F.~Zhang, S.~Chamberlain.
\newblock The geometry of uncertainty in moving objects databases.
\newblock In {\em EDBT}, pp. 233--250, 2001.

\bibitem{pelekis2009clustering}
N.~Pelekis, I.~Kopanakis, E.~Kotsifakos, E.~Frentzos, Y.~Theodoridis.
\newblock Clustering Trajectories of Moving Objects in an Uncertain World.
\newblock In {\em ICDM}, pp. 417--427, 2009.

\bibitem{zhang2009effectively}
M.~Zhang, S.~Chen, C.S.~Jensen, B.C.~Ooi, Z.~Zhang.
\newblock Effectively indexing uncertain moving objects for predictive queries.
\newblock In {\em VLDB}, pp. 1198--1209, 2009.

\bibitem{ding2008utr}
Z.~Ding.
\newblock UTR-tree: An index structure for the full uncertain trajectories of network-constrained moving objects.
\newblock In {\em MDM}, pp. 33--40, 2008.

\bibitem{ding2004uncertainty}
Z.~Ding, R.H.~G{\"u}ting.
\newblock Uncertainty management for network constrained moving objects.
\newblock In {\em DEXA}, pp. 411-421, 2004.

\bibitem{lamarca2008location}
A.~LaMarca, E.~De Lara.
\newblock Location systems: An introduction to the technology behind location awareness.
\newblock In {\em Synthesis Lectures on Mobile and Pervasive Computing}, pp. 1--122, 2008.

\bibitem{tran2009probabilistic}
T.~Tran, C.~Sutton, R.~Cocci, Y.~Nie, Y.~Diao, P.~Shenoy.
\newblock Probabilistic inference over RFID streams in mobile environments.
\newblock In {\em ICDE}, pp. 1096--1107, 2009.

\bibitem{brakatsoulas2005map}
S.~Brakatsoulas, D.~Pfoser, R.~Salas, C.~Wenk.
\newblock On map-matching vehicle tracking data.
\newblock In {\em VLDB}, pp. 853--864, 2005.

\bibitem{bessho2009location}
M.~Bessho, N.~Koshizuka, S.~Kobayashi, K.~Sakamura.
\newblock Location systems for ubiquitous computing.
\newblock In {\em Journal of IEICE}, pp. 249--255, 2009.

\bibitem{shumway2010time}
R.H.~Shumway, D.S.~Stoffer.
\newblock Time Series Analysis and Its Applications.
\newblock In {\em Springer Science \& Business Media}, 2010.

\bibitem{bauwens2006multivariate}
L.~Bauwens, S.~Laurent, VK.~Jeroen.
\newblock Multivariate GARCH models: a survey.
\newblock In {\em Journal of applied econometrics}, pp. 79--109, 2006.

}
\end{thebibliography}

\end{frame}
