%------------------------------------------------

\begin{frame}[allowframebreaks]
\frametitle{References}

\begin{thebibliography}{99} % Beamer does not support BibTeX so references must be inserted manually as below
\bibliographystyle{abbrv}
\fsize{

\bibitem{DBLP:conf/mdm/JensenLY09}
C.~S. Jensen, H.~Lu, and B.~Yang.
\newblock Graph model based indoor tracking.
\newblock In {\em {MDM}}, pp. 122--131, 2009.

\bibitem{DBLP:conf/cikm/YangLJ09}
B.~Yang, H.~Lu, and C.~S. Jensen.
\newblock Scalable continuous range monitoring of moving objects in symbolic
  indoor space.
\newblock In {\em CIKM}, pp. 671--680, 2009.

\bibitem{DBLP:conf/edbt/YangLJ10}
B.~Yang, H.~Lu, and C.~S. Jensen.
\newblock Probabilistic threshold k nearest neighbor queries over moving
  objects in symbolic indoor space.
\newblock In {\em EDBT}, pp. 335--346, 2010.

\bibitem{DBLP:conf/icde/LuYCJ11}
H.~Lu, B.~Yang, and C.~S. Jensen.
\newblock Spatio-temporal Joins on Symbolic Indoor Tracking Data.
\newblock In {\em {ICDE}}, pp. 816--827, 2011.

\bibitem{jensen2010indoor}
C.~S. Jensen, H.~Lu and B.~Yang.
\newblock Indoor-A New Data Management Frontier.
\newblock In {\em IEEE Data Eng. Bull.}, pp. 12--17, 2010.

\bibitem{DBLP:conf/icde/LuCJ12}
H.~Lu, X.~Cao, and C.~S. Jensen.
\newblock A foundation for efficient indoor distance-aware query processing.
\newblock In {\em ICDE}, pp. 438--449, 2012.

\bibitem{becker2005location}
C.~Becker and F.~D{\"u}rr.
\newblock On location models for ubiquitous computing.
\newblock In {\em Personal and Ubiquitous Computing}, pp. 20--31, 2005.

\bibitem{li2008lattice}
D.~Li and D.~L.~Lee.
\newblock A lattice-based semantic location model for indoor navigation.
\newblock In {\em MDM}, pp. 17--24, 2008.

\bibitem{becker2009multilayered}
T.~Becker, C.~Nagel and T.~H.~Kolbe
\newblock A multilayered space-event model for navigation in indoor spaces.
\newblock In {\em 3D Geo-Information Sciences}, pp. 61--77, 2009.

}
\end{thebibliography}

\end{frame}
