%------------------------------------------------

\begin{frame}[allowframebreaks]
\frametitle{References}

\begin{thebibliography}{99} % Beamer does not support BibTeX so references must be inserted manually as below
\bibliographystyle{abbrv}
\fsize{

\bibitem{DBLP:conf/edbt/YangLJ10}
B.~Yang, H.~Lu, C.S.~Jensen.
\newblock Probabilistic threshold k nearest neighbor queries over moving objects in symbolic indoor space.
\newblock In {\em EDBT}, pp. 335--346, 2010.

\bibitem{DBLP:conf/icde/LuCJ12}
H.~Lu, X.~Cao, C.S.~Jensen.
\newblock A foundation for efficient indoor distance-aware query processing.
\newblock In {\em ICDE}, pp. 438--449, 2012.

\bibitem{DBLP:conf/icde/XieLP13}
X.~Xie, H.~Lu, T.B.~Pedersen.
\newblock Efficient distance-aware query evaluation on indoor moving objects.
\newblock In {\em ICDE}, pp. 434--445, 2013.

\bibitem{pfoser1999capturing}
D.~Pfoser, C.S.~Jensen.
\newblock Capturing the uncertainty of moving-object representations
\newblock In {\em Advances in Spatial Databases}, pp. 111--131, 1999.

\bibitem{cheng2003evaluating}
R.~Cheng, D.V.~Kalashnikov, S.~Prabhakar.
\newblock Evaluating probabilistic queries over imprecise data.
\newblock In {\em SIGMOD}, pp. 551--562, 2003.

\bibitem{cheng2004querying}
R.~Cheng, D.V.~Kalashnikov, S.~Prabhakar.
\newblock Querying imprecise data in moving object environments.
\newblock In {\em TKDE}, pp. 1112--1127, 2004.

\bibitem{kriegel2007probabilistic}
H.-P.~Kriegel, P.~Kunath, M.~Renz.
\newblock Probabilistic nearest-neighbor query on uncertain objects.
\newblock In {\em DSAFAA}, pp. 337--348, 2007.

}
\end{thebibliography}

\end{frame}
