%------------------------------------------------

\begin{frame}[allowframebreaks]
\frametitle{References}

\begin{thebibliography}{99} % Beamer does not support BibTeX so references must be inserted manually as below
\bibliographystyle{abbrv}
\fsize{

\bibitem{baba2016learning}
A.I.~Baba, M.~Jaeger, H.~Lu, T.B.~Pedersen, W-S.~Ku, X.~Xie.
\newblock Learning-Based Cleansing for Indoor RFID Data.
\newblock In {\em SIGMOD}, 2016.

\bibitem{chen2010leveraging}
H.~Chen, W-S.~Ku, H.~Wang, M-T.~Sun.
\newblock Leveraging spatio-temporal redundancy for RFID data cleansing.
\newblock In {\em SIGMOD}, pp. 51--62, 2010.

\bibitem{baba2013spatiotemporal}
A.I.~Baba, H.~Lu, X.~Xie, T.B.~Pedersen.
\newblock Spatiotemporal data cleansing for indoor RFID tracking data.
\newblock In {\em MDM}, pp. 187--196, 2013.

\bibitem{baba2013graph}
A.I.~Baba, H.~Lu, T.B.~Pedersen, X.~Xie.
\newblock A graph model for false negative handling in indoor RFID tracking data.
\newblock In {\em SIGSPATIAL}, pp. 464--467, 2013.

\bibitem{tran2009probabilistic}
T.~Tran, C.~Sutton, R.~Cocci, Y.~Nie, Y.~Diao, P.~Shenoy.
\newblock Probabilistic inference over RFID streams in mobile environments.
\newblock In {\em ICDE}, pp. 1096--1107, 2009.

\bibitem{DBLP:conf/edbt/FazzingaFFP14}
B.~Fazzinga, S.~Flesca, F.~Furfaro, F.~Parisi.
\newblock Cleaning Trajectory Data of RFID-monitored Objects through Conditioning under Integrity Constraints.
\newblock In {\em EDBT}, pp. 379--390, 2014.

\bibitem{nie2009probabilistic}
Y.~Nie, Z.~Li, S.~Peng, Q.~Chen.
\newblock Probabilistic Modeling of Streaming RFID Data by Using Correlated Variable-duration HMMs.
\newblock In {SERA}, pp. 72--77, 2009.

\bibitem{kirshner2005modeling}
S.~Kirshner.
\newblock Modeling of multivariate time series using hidden Markov models.
\newblock PhD thesis, Long Beach, CA, USA, 2005.

\bibitem{viterbi1967error}
A J.~Viterbi.
\newblock Error bounds for convolutional codes and an asymptotically optimum decoding algorithm.
\newblock In {{IEEE} Trans. Information Theory}, pp. 13(2):260--269, 1967.


% \bibitem{koch2008conditioning}
% C.~Koch, D.~Olteanu.
% \newblock Conditioning probabilistic databases.
% \newblock In {\em VLDB}, pp. 313--325, 2008.

%
% \bibitem{floerkemeier2004issues}
% C.~Floerkemeier, M.~Lampe.
% \newblock Issues with RFID usage in ubiquitous computing applications.
% \newblock In {\em Pervasive Computing}, pp. 188--193, 2004.
%
% \bibitem{derakhshan2007rfid}
% R.~Derakhshan, M.E.~Orlowska, X.~Li.
% \newblock RFID data management: challenges and opportunities.
% \newblock In {\em IEEE International conference on RFID}, vol. 10, 2007.
%
% \bibitem{DBLP:conf/icde/LuCJ12}
% H.~Lu, X.~Cao, and C.~S. Jensen.
% \newblock A foundation for efficient indoor distance-aware query processing.
% \newblock In {\em ICDE}, pp. 438--449, 2012.
%
% \bibitem{baba2014handling}
% A.I.~Baba, H.~Lu, T.B.~Pedersen, X.~Xie.
% \newblock Handling false negatives in indoor RFID data.
% \newblock In {\em MDM}, pp. 117--126, 2014.

}
\end{thebibliography}

\end{frame}
